### 2017-04-01 Writing/rsptime.tex
Update

\subsection{Running Code Fingerprint}
Fingerprints the code running on a device, which leads to plaintext recovery.
\begin{itemize}
	\item Theory explained in \Cref{FingerprintTheory}.
	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
	\item Not for 802.15.4: adversary can't join the network.
	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
\end{itemize}

\AddFigure{fig/PingProbe_Session.png}{How fingerprint works}{FingerprintTheory}

>>>>

\subsection{Running Code Fingerprint}
%Fingerprints the code running on a device, which leads to plaintext recovery.
%\begin{itemize}
%	\item Theory explained in \Cref{FingerprintTheory}.
%	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
%	\item Not for 802.15.4: adversary can't join the network.
%	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
%\end{itemize}
The response time of packets can also be exploited to fingerprint the code running on a specific device. \Cref{FingerprintTheory} demonstrates the fundamental idea of the code fingerprinting attack.

\begin{figure}
	\center
	\includegraphics[width=\textwidth]{fig/PingProbe_Theory.png}
	\caption{Variations in PING Response Latency\label{FingerprintTheory}}
\end{figure}

%How it works

%What can be the Request

%Experiment Result
